Bayesian 5 taxa family

### 2021-03-09 scripts/44_ggplot_venn_lefse.Rmd
udpate

all_title_fs <- 20
axis_text_fs <- 16
make %>% 
  split(.$outcome) %>% 
  imap(~   ggplot(data = .x, aes(x = reorder(feature, score), y = score, fill = direction)) +
            geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
            coord_flip() +
            #scale_color_manual(values = c('#0099B4', '#AD002A'))  +
            #scale_fill_manual(values = c('#0099B4', '#AD002A')) +
            theme_classic() +
            theme(axis.title.y  = element_blank(), 
                  axis.title.x = element_text(size=axis_text_fs),
                  plot.title = element_text(size=all_title_fs),
                  axis.text.x = element_text(size=axis_text_fs),
                  legend.position="bottom") +
         scale_fill_manual(values = c('#0099B4','#AD002A')) +
            labs(title = str_glue('Response to {.y}') ,
                 y = 'Score')+ 
            ggsave(str_glue('../data/shotgun_output/humann3/pull_{.y}_pathway.pdf'), device = 'pdf', width = 8))
            #ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/shotgun_results/NEW_humann3_version/pathway/pull_{.y}_pathway.pdf'), device = 'pdf', width = 12))

>>>>

all_title_fs <- 20
axis_text_fs <- 16
make %>% 
  split(.$outcome) %>% 
  imap(~   ggplot(data = .x, aes(x = reorder(feature, score), y = score, fill = direction)) +
            geom_col(position = position_dodge2(width = 0.9, preserve = "single")) +
            coord_flip() +
            #scale_color_manual(values = c('#0099B4', '#AD002A'))  +
            #scale_fill_manual(values = c('#0099B4', '#AD002A')) +
            theme_classic() +
            theme(axis.title.y  = element_blank(), 
                  axis.title.x = element_text(size=axis_text_fs),
                  plot.title = element_text(size=all_title_fs),
                  axis.text.x = element_text(size=axis_text_fs),
                  legend.position="bottom") +
         scale_fill_manual(values = c('#0099B4','#AD002A')) +
            labs(title = str_glue('Response to {.y}') ,
                 y = 'Score')+ 
            ggsave(str_glue('../data/shotgun_output/humann3/pull_{.y}_pathway.pdf'), device = 'pdf', width = 12, height = 20))
            #ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/shotgun_results/NEW_humann3_version/pathway/pull_{.y}_pathway.pdf'), device = 'pdf', width = 12))

### 2021-03-09 scripts/53_bayesian_5fam.Rmd
udpate

---
title: "Bayesian 5 taxa family"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

Model:
- CR_d100 ~ Faecalibacterium + Ruminococcus + Akkermansia + Bacteroides + Enterococcus

@@

```{r}
# the model
tox <- brm( toxicity  ~ 
              Akkermansia +
              Bacteroides +
              Enterococcus +
              Faecalibacterium +
              Ruminococcus +
               (1 | pt_id) ,  
              data = dat, 
              family = bernoulli(), 
              warmup = 1000, iter = 3000, 
              cores = 8, chains = 4, 
              seed = 123)
```

>>>>

---
title: "Bayesian 5 taxa family"
author: "Anqi Dai"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

@@

Model:

- CR_d100 ~ Faecalibacterium + Ruminococcus + Akkermansia + Bacteroides + Enterococcus

@@

```{r}
# the model 
tox <- brm( toxicity  ~ 
              Akkermansia +
              Bacteroides +
              Enterococcus +
              Faecalibacterium +
              Ruminococcus +
               (1 | pt_id) ,  
              data = dat, 
              family = bernoulli(), 
              warmup = 5000, iter = 40000, 
              cores = 8, chains = 2, 
              seed = 123)

# It's giving errors: "Effective Samples Size (ESS) is too low, indicating posterior means and medians may be unreliable.
# Running the chains for more iterations may help"
```

```{r}
# Sean suggested to use individual genus first, good idea. 
# do 5 iteratively in a loop
target <- c('Akkermansia','Bacteroides','Enterococcus','Faecalibacterium','Ruminococcus')

ret <- target %>% 
  set_names(target) %>% 
  map(function(genus) {
      mod =  brm( as.formula(str_glue('toxicity  ~ 
              {genus} +
               (1 | pt_id)')),  
             data = dat, 
              family = bernoulli(), 
              warmup = 3000, iter = 10000, 
              cores = 8, chains = 2, 
              seed = 123)

      res = posterior_samples(mod) %>% 
              select(starts_with('b')) %>% 
              select(-b_Intercept)
      return(res)
  }) %>% 
  bind_cols()

```
